---
title: "CPSC 540 - Homework 1: Marketing Campaign Analysis"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: flatly
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center',
  fig.width = 10,
  fig.height = 6,
  tidy = TRUE,
  size = "vsmall"
)

# Set seed for reproducibility
set.seed(1818)

# Set options
options(width = 70)
options(scipen = 99)
```

```{r load-packages}
# Load required packages
library(tidyverse)      # Data manipulation and visualization
library(broom)          # Tidy model outputs
library(MASS)           # For negative binomial and other GLMs
library(car)            # For VIF and diagnostic tests
library(GGally)         # For ggpairs plots
library(gridExtra)      # For arranging multiple plots
library(scales)         # For formatting scales
library(viridis)        # For color palettes
library(effectsize)     # For effect size calculations
library(performance)    # For model diagnostics
library(see)            # For enhanced visualizations
```

# 1. Data Loading and Initial Exploration

## 1.1 Load Data

```{r load-data}
# Load the marketing campaign data
data <- read.csv("marketingcampaign.csv")

# Display first few rows
head(data)

# Display structure
str(data)

# Display summary statistics
summary(data)
```

## 1.2 Data Dimensions and Missing Values

```{r data-overview}
# Check dimensions
cat("Dataset dimensions:", nrow(data), "rows and", ncol(data), "columns\n")

# Check for missing values
missing_summary <- data %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Missing_Count") %>%
  mutate(Missing_Percent = (Missing_Count / nrow(data)) * 100)

print(missing_summary)

# Total missing values
cat("\nTotal missing values:", sum(is.na(data)), "\n")
```

## 1.3 Convert Variables to Appropriate Types

```{r data-prep}
# Convert categorical variables to factors
data <- data %>%
  mutate(
    gender = factor(gender),
    campaign_variant = factor(campaign_variant, levels = c("A", "B", "C")),
    ad_source = factor(ad_source),
    email_signup = factor(email_signup)
  )

# Verify conversions
str(data)
```

# 2. Exploratory Data Analysis (EDA)

## 2.1 Distribution of Continuous Variables

```{r continuous-distributions, fig.height=8}
# Create histograms for continuous variables
p1 <- ggplot(data, aes(x = age)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "black", alpha = 0.7) +
  geom_vline(aes(xintercept = mean(age)), color = "red", linetype = "dashed", size = 1) +
  labs(title = "Distribution of Age", x = "Age", y = "Count") +
  theme_minimal()

p2 <- ggplot(data, aes(x = past_purchases)) +
  geom_histogram(bins = 30, fill = "forestgreen", color = "black", alpha = 0.7) +
  geom_vline(aes(xintercept = mean(past_purchases)), color = "red", linetype = "dashed", size = 1) +
  labs(title = "Distribution of Past Purchases", x = "Past Purchases", y = "Count") +
  theme_minimal()

p3 <- ggplot(data, aes(x = campaign_spend)) +
  geom_histogram(bins = 30, fill = "coral", color = "black", alpha = 0.7) +
  geom_vline(aes(xintercept = mean(campaign_spend)), color = "red", linetype = "dashed", size = 1) +
  labs(title = "Distribution of Campaign Spend", x = "Campaign Spend ($)", y = "Count") +
  theme_minimal()

grid.arrange(p1, p2, p3, ncol = 1)
```

```{r continuous-summary}
# Summary statistics for continuous variables
data %>%
  select(age, past_purchases, campaign_spend) %>%
  summarise(
    across(everything(),
           list(
             mean = ~mean(., na.rm = TRUE),
             median = ~median(., na.rm = TRUE),
             sd = ~sd(., na.rm = TRUE),
             min = ~min(., na.rm = TRUE),
             max = ~max(., na.rm = TRUE)
           ))
  ) %>%
  pivot_longer(everything(), names_to = c("Variable", "Statistic"), names_sep = "_") %>%
  pivot_wider(names_from = Statistic, values_from = value)
```

## 2.2 Distribution of Categorical Variables

```{r categorical-distributions, fig.height=8}
# Bar plots for categorical variables
p4 <- ggplot(data, aes(x = gender, fill = gender)) +
  geom_bar(alpha = 0.7, color = "black") +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  scale_fill_viridis_d() +
  labs(title = "Distribution of Gender", x = "Gender", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p5 <- ggplot(data, aes(x = campaign_variant, fill = campaign_variant)) +
  geom_bar(alpha = 0.7, color = "black") +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  scale_fill_manual(values = c("A" = "#E69F00", "B" = "#56B4E9", "C" = "#009E73")) +
  labs(title = "Distribution of Campaign Variant", x = "Campaign Variant", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

p6 <- ggplot(data, aes(x = ad_source, fill = ad_source)) +
  geom_bar(alpha = 0.7, color = "black") +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  scale_fill_viridis_d() +
  labs(title = "Distribution of Ad Source", x = "Ad Source", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))

p7 <- ggplot(data, aes(x = email_signup, fill = email_signup)) +
  geom_bar(alpha = 0.7, color = "black") +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  scale_fill_manual(values = c("TRUE" = "darkgreen", "FALSE" = "darkred")) +
  labs(title = "Distribution of Email Signup", x = "Email Signup", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")

grid.arrange(p4, p5, p6, p7, ncol = 2)
```

```{r categorical-summary}
# Frequency tables for categorical variables
cat("Gender Distribution:\n")
print(table(data$gender))
cat("\nCampaign Variant Distribution:\n")
print(table(data$campaign_variant))
cat("\nAd Source Distribution:\n")
print(table(data$ad_source))
cat("\nEmail Signup Distribution:\n")
print(table(data$email_signup))
```

## 2.3 Correlations and Relationships

```{r correlation-plot, fig.height=8, fig.width=10}
# Select numeric variables for correlation
numeric_vars <- data %>% select(age, past_purchases, campaign_spend)

# Create correlation matrix
cor_matrix <- cor(numeric_vars, use = "complete.obs")
print(cor_matrix)

# Visualize correlations
ggpairs(numeric_vars,
        title = "Pairwise Relationships of Numeric Variables",
        lower = list(continuous = wrap("points", alpha = 0.3, size = 0.5)),
        diag = list(continuous = wrap("densityDiag", alpha = 0.5))) +
  theme_minimal()
```

# 3. Question 1: What kinds of people make MORE purchases?

**Research Question**: Identify demographic and behavioral characteristics associated with higher past purchase counts.

## 3.1 Exploratory Analysis for Question 1

```{r q1-exploration, fig.height=10}
# Past purchases by gender
p8 <- ggplot(data, aes(x = gender, y = past_purchases, fill = gender)) +
  geom_boxplot(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 0.5) +
  scale_fill_viridis_d() +
  labs(title = "Past Purchases by Gender", x = "Gender", y = "Past Purchases") +
  theme_minimal() +
  theme(legend.position = "none")

# Past purchases by age
p9 <- ggplot(data, aes(x = age, y = past_purchases)) +
  geom_point(alpha = 0.3, color = "steelblue") +
  geom_smooth(method = "loess", color = "red", size = 1.5) +
  labs(title = "Past Purchases vs Age", x = "Age", y = "Past Purchases") +
  theme_minimal()

# Past purchases by email signup
p10 <- ggplot(data, aes(x = email_signup, y = past_purchases, fill = email_signup)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = c("TRUE" = "darkgreen", "FALSE" = "darkred")) +
  labs(title = "Past Purchases by Email Signup Status", x = "Email Signup", y = "Past Purchases") +
  theme_minimal() +
  theme(legend.position = "none")

# Past purchases by ad source
p11 <- ggplot(data, aes(x = ad_source, y = past_purchases, fill = ad_source)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_viridis_d() +
  labs(title = "Past Purchases by Ad Source", x = "Ad Source", y = "Past Purchases") +
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(p8, p9, p10, p11, ncol = 2)
```

```{r q1-summary-stats}
# Summary statistics by groups
cat("Mean Past Purchases by Gender:\n")
data %>%
  group_by(gender) %>%
  summarise(
    mean_purchases = mean(past_purchases),
    median_purchases = median(past_purchases),
    sd_purchases = sd(past_purchases),
    n = n()
  ) %>%
  print()

cat("\nMean Past Purchases by Email Signup:\n")
data %>%
  group_by(email_signup) %>%
  summarise(
    mean_purchases = mean(past_purchases),
    median_purchases = median(past_purchases),
    sd_purchases = sd(past_purchases),
    n = n()
  ) %>%
  print()

cat("\nMean Past Purchases by Ad Source:\n")
data %>%
  group_by(ad_source) %>%
  summarise(
    mean_purchases = mean(past_purchases),
    median_purchases = median(past_purchases),
    sd_purchases = sd(past_purchases),
    n = n()
  ) %>%
  arrange(desc(mean_purchases)) %>%
  print()
```

## 3.2 Statistical Modeling for Question 1

Since `past_purchases` is a count variable (non-negative integers), we'll use **Poisson Regression** or **Negative Binomial Regression**.

```{r q1-check-overdispersion}
# Check mean and variance of past_purchases
mean_purchases <- mean(data$past_purchases)
var_purchases <- var(data$past_purchases)

cat("Mean of past_purchases:", mean_purchases, "\n")
cat("Variance of past_purchases:", var_purchases, "\n")
cat("Variance/Mean ratio:", var_purchases / mean_purchases, "\n")

# If variance >> mean, we have overdispersion and should use Negative Binomial
```

### 3.2.1 Poisson Regression Model

```{r q1-poisson-model}
# Fit Poisson regression model
poisson_model <- glm(past_purchases ~ age + gender + email_signup + ad_source,
                     data = data,
                     family = poisson(link = "log"))

# Model summary
summary(poisson_model)

# Tidy output
tidy_poisson <- tidy(poisson_model, conf.int = TRUE, exponentiate = TRUE)
print(tidy_poisson)
```

### 3.2.2 Negative Binomial Regression Model

```{r q1-negbin-model}
# Fit Negative Binomial regression model (handles overdispersion)
negbin_model <- glm.nb(past_purchases ~ age + gender + email_signup + ad_source,
                       data = data)

# Model summary
summary(negbin_model)

# Tidy output with exponentiated coefficients (Incident Rate Ratios)
tidy_negbin <- tidy(negbin_model, conf.int = TRUE, exponentiate = TRUE)
print(tidy_negbin)
```

### 3.2.3 Model Comparison

```{r q1-model-comparison}
# Compare models using AIC
cat("Poisson Model AIC:", AIC(poisson_model), "\n")
cat("Negative Binomial Model AIC:", AIC(negbin_model), "\n")

# Likelihood ratio test
anova(poisson_model, negbin_model)

# Choose the better model (lower AIC is better)
if(AIC(negbin_model) < AIC(poisson_model)) {
  best_model_q1 <- negbin_model
  cat("\nNegative Binomial model is preferred (better handles overdispersion)\n")
} else {
  best_model_q1 <- poisson_model
  cat("\nPoisson model is preferred\n")
}
```

### 3.2.4 Model Diagnostics

```{r q1-diagnostics, fig.height=8}
# Residual plots
par(mfrow = c(2, 2))
plot(best_model_q1)
par(mfrow = c(1, 1))

# Check for multicollinearity
cat("\nVariance Inflation Factors (VIF):\n")
print(vif(best_model_q1))
```

### 3.2.5 Effect Visualization

```{r q1-effects-plot, fig.height=10}
# Extract coefficients for plotting (excluding intercept)
coef_plot_data <- tidy_negbin %>%
  filter(term != "(Intercept)") %>%
  mutate(term = fct_reorder(term, estimate))

# Plot Incident Rate Ratios
p12 <- ggplot(coef_plot_data, aes(x = estimate, y = term)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 1) +
  geom_point(size = 4, color = "steelblue") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2, size = 1) +
  labs(
    title = "Incident Rate Ratios for Past Purchases",
    subtitle = "Negative Binomial Regression Coefficients (95% CI)",
    x = "Incident Rate Ratio (IRR)",
    y = "Predictor"
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 10))

print(p12)

# Predicted values by age
age_pred <- data.frame(
  age = seq(min(data$age), max(data$age), length.out = 100),
  gender = "Man",
  email_signup = "TRUE",
  ad_source = "Facebook"
)
age_pred$predicted <- predict(best_model_q1, newdata = age_pred, type = "response")

p13 <- ggplot() +
  geom_point(data = data, aes(x = age, y = past_purchases), alpha = 0.2, color = "gray") +
  geom_line(data = age_pred, aes(x = age, y = predicted), color = "red", size = 1.5) +
  labs(
    title = "Predicted Past Purchases by Age",
    subtitle = "Holding other variables constant",
    x = "Age",
    y = "Predicted Past Purchases"
  ) +
  theme_minimal()

print(p13)
```

# 4. Question 2: Which campaign variant should Company X use?

**Research Question**: Determine which campaign variant (A, B, or C) results in the highest campaign spending.

## 4.1 Exploratory Analysis for Question 2

```{r q2-exploration, fig.height=10}
# Campaign spend by variant
p14 <- ggplot(data, aes(x = campaign_variant, y = campaign_spend, fill = campaign_variant)) +
  geom_boxplot(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 0.5) +
  scale_fill_manual(values = c("A" = "#E69F00", "B" = "#56B4E9", "C" = "#009E73")) +
  labs(title = "Campaign Spend by Variant", x = "Campaign Variant", y = "Campaign Spend ($)") +
  theme_minimal() +
  theme(legend.position = "none")

# Campaign spend by variant and gender
p15 <- ggplot(data, aes(x = campaign_variant, y = campaign_spend, fill = gender)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_viridis_d() +
  labs(title = "Campaign Spend by Variant and Gender",
       x = "Campaign Variant",
       y = "Campaign Spend ($)") +
  theme_minimal()

# Campaign spend by variant and email signup
p16 <- ggplot(data, aes(x = campaign_variant, y = campaign_spend, fill = email_signup)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = c("TRUE" = "darkgreen", "FALSE" = "darkred")) +
  labs(title = "Campaign Spend by Variant and Email Signup",
       x = "Campaign Variant",
       y = "Campaign Spend ($)") +
  theme_minimal()

# Mean campaign spend by variant
p17 <- data %>%
  group_by(campaign_variant) %>%
  summarise(
    mean_spend = mean(campaign_spend),
    se = sd(campaign_spend) / sqrt(n())
  ) %>%
  ggplot(aes(x = campaign_variant, y = mean_spend, fill = campaign_variant)) +
  geom_col(alpha = 0.7, color = "black") +
  geom_errorbar(aes(ymin = mean_spend - 1.96*se, ymax = mean_spend + 1.96*se),
                width = 0.2, size = 1) +
  geom_text(aes(label = paste0("$", round(mean_spend, 2))), vjust = -2.5) +
  scale_fill_manual(values = c("A" = "#E69F00", "B" = "#56B4E9", "C" = "#009E73")) +
  labs(title = "Mean Campaign Spend by Variant (with 95% CI)",
       x = "Campaign Variant",
       y = "Mean Campaign Spend ($)") +
  theme_minimal() +
  theme(legend.position = "none")

grid.arrange(p14, p15, p16, p17, ncol = 2)
```

```{r q2-summary-stats}
# Detailed summary statistics by campaign variant
cat("Campaign Spend Summary by Variant:\n")
campaign_summary <- data %>%
  group_by(campaign_variant) %>%
  summarise(
    n = n(),
    mean_spend = mean(campaign_spend),
    median_spend = median(campaign_spend),
    sd_spend = sd(campaign_spend),
    min_spend = min(campaign_spend),
    max_spend = max(campaign_spend),
    total_spend = sum(campaign_spend)
  ) %>%
  arrange(desc(mean_spend))

print(campaign_summary)

# Test for differences (ANOVA)
cat("\nOne-way ANOVA test:\n")
anova_result <- aov(campaign_spend ~ campaign_variant, data = data)
print(summary(anova_result))
```

## 4.2 Statistical Modeling for Question 2

Campaign spend is a continuous positive variable. We'll use **Linear Regression** and potentially **Gamma Regression** (for positive continuous data).

### 4.2.1 Linear Regression Model

```{r q2-linear-model}
# Fit linear regression model
linear_model_q2 <- lm(campaign_spend ~ campaign_variant + age + gender +
                       past_purchases + email_signup + ad_source,
                     data = data)

# Model summary
summary(linear_model_q2)

# Tidy output
tidy_linear_q2 <- tidy(linear_model_q2, conf.int = TRUE)
print(tidy_linear_q2)
```

### 4.2.2 Gamma Regression Model

```{r q2-gamma-model}
# Fit Gamma GLM (for positive continuous outcomes)
gamma_model_q2 <- glm(campaign_spend ~ campaign_variant + age + gender +
                       past_purchases + email_signup + ad_source,
                     data = data,
                     family = Gamma(link = "log"))

# Model summary
summary(gamma_model_q2)

# Tidy output with exponentiated coefficients
tidy_gamma_q2 <- tidy(gamma_model_q2, conf.int = TRUE, exponentiate = TRUE)
print(tidy_gamma_q2)
```

### 4.2.3 Model Comparison

```{r q2-model-comparison}
# Compare models using AIC
cat("Linear Model AIC:", AIC(linear_model_q2), "\n")
cat("Gamma Model AIC:", AIC(gamma_model_q2), "\n")

# Choose the better model
if(AIC(gamma_model_q2) < AIC(linear_model_q2)) {
  best_model_q2 <- gamma_model_q2
  cat("\nGamma model is preferred\n")
} else {
  best_model_q2 <- linear_model_q2
  cat("\nLinear model is preferred\n")
}
```

### 4.2.4 Model Diagnostics

```{r q2-diagnostics, fig.height=8}
# Residual plots
par(mfrow = c(2, 2))
plot(linear_model_q2)
par(mfrow = c(1, 1))

# Check for multicollinearity
cat("\nVariance Inflation Factors (VIF):\n")
print(vif(linear_model_q2))
```

### 4.2.5 Post-hoc Analysis: Pairwise Comparisons

```{r q2-posthoc}
# Tukey HSD for pairwise comparisons
cat("Tukey's HSD Test for Campaign Variants:\n")
tukey_result <- TukeyHSD(anova_result)
print(tukey_result)

# Visualize Tukey results
plot(tukey_result, las = 1, col = "steelblue")
```

### 4.2.6 Effect Visualization

```{r q2-effects-plot, fig.height=10}
# Extract campaign variant coefficients
campaign_coefs <- tidy_linear_q2 %>%
  filter(str_detect(term, "campaign_variant"))

# Plot campaign variant effects
p18 <- ggplot(campaign_coefs, aes(x = estimate, y = term)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red", size = 1) +
  geom_point(size = 4, color = "steelblue") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2, size = 1) +
  labs(
    title = "Campaign Variant Effects on Spend",
    subtitle = "Linear Regression Coefficients (95% CI) - Relative to Variant A",
    x = "Effect on Campaign Spend ($)",
    y = "Campaign Variant"
  ) +
  theme_minimal()

print(p18)

# Predicted campaign spend by variant (marginal means)
predicted_by_variant <- data %>%
  group_by(campaign_variant) %>%
  mutate(predicted = predict(linear_model_q2, newdata = cur_data(), type = "response")) %>%
  group_by(campaign_variant) %>%
  summarise(
    mean_predicted = mean(predicted),
    se = sd(predicted) / sqrt(n())
  )

p19 <- ggplot(predicted_by_variant, aes(x = campaign_variant, y = mean_predicted, fill = campaign_variant)) +
  geom_col(alpha = 0.7, color = "black") +
  geom_errorbar(aes(ymin = mean_predicted - 1.96*se, ymax = mean_predicted + 1.96*se),
                width = 0.2, size = 1) +
  geom_text(aes(label = paste0("$", round(mean_predicted, 2))), vjust = -2) +
  scale_fill_manual(values = c("A" = "#E69F00", "B" = "#56B4E9", "C" = "#009E73")) +
  labs(
    title = "Model-Predicted Campaign Spend by Variant",
    subtitle = "Adjusted for covariates (95% CI)",
    x = "Campaign Variant",
    y = "Predicted Campaign Spend ($)"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

print(p19)
```

# 5. Additional Analyses

## 5.1 Interaction Effects

Are there interactions between campaign variant and customer characteristics?

```{r interaction-analysis, fig.height=8}
# Test interaction between campaign variant and email signup
interaction_model <- lm(campaign_spend ~ campaign_variant * email_signup +
                         age + gender + past_purchases + ad_source,
                       data = data)

summary(interaction_model)

# Visualize interaction
interaction_plot <- data %>%
  group_by(campaign_variant, email_signup) %>%
  summarise(
    mean_spend = mean(campaign_spend),
    se = sd(campaign_spend) / sqrt(n())
  )

ggplot(interaction_plot, aes(x = campaign_variant, y = mean_spend,
                             color = email_signup, group = email_signup)) +
  geom_line(size = 1.5) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_spend - 1.96*se, ymax = mean_spend + 1.96*se),
                width = 0.1) +
  scale_color_manual(values = c("TRUE" = "darkgreen", "FALSE" = "darkred")) +
  labs(
    title = "Campaign Spend: Variant × Email Signup Interaction",
    x = "Campaign Variant",
    y = "Mean Campaign Spend ($)",
    color = "Email Signup"
  ) +
  theme_minimal()
```

## 5.2 Customer Segments

```{r customer-segments, fig.height=6}
# Create customer segments based on purchase behavior
data <- data %>%
  mutate(
    purchase_segment = case_when(
      past_purchases <= quantile(past_purchases, 0.33) ~ "Low",
      past_purchases <= quantile(past_purchases, 0.67) ~ "Medium",
      TRUE ~ "High"
    ),
    purchase_segment = factor(purchase_segment, levels = c("Low", "Medium", "High"))
  )

# Campaign spend by segment and variant
ggplot(data, aes(x = campaign_variant, y = campaign_spend, fill = purchase_segment)) +
  geom_boxplot(alpha = 0.7) +
  scale_fill_manual(values = c("Low" = "#d7191c", "Medium" = "#fdae61", "High" = "#1a9641")) +
  labs(
    title = "Campaign Spend by Variant and Purchase Segment",
    x = "Campaign Variant",
    y = "Campaign Spend ($)",
    fill = "Purchase Segment"
  ) +
  theme_minimal()
```

# 6. Summary and Key Findings

## Question 1: What kinds of people make more purchases?

```{r q1-summary}
# Display key predictors
cat("Key Findings for Question 1:\n\n")

significant_predictors_q1 <- tidy_negbin %>%
  filter(p.value < 0.05, term != "(Intercept)") %>%
  arrange(p.value) %>%
  mutate(
    interpretation = case_when(
      estimate > 1 ~ paste0("Increases purchases by ", round((estimate - 1) * 100, 1), "%"),
      estimate < 1 ~ paste0("Decreases purchases by ", round((1 - estimate) * 100, 1), "%"),
      TRUE ~ "No effect"
    )
  ) %>%
  select(term, estimate, p.value, interpretation)

print(significant_predictors_q1)
```

## Question 2: Which campaign variant should Company X use?

```{r q2-summary}
# Display campaign variant comparison
cat("Key Findings for Question 2:\n\n")

# Calculate ROI metrics
campaign_roi <- campaign_summary %>%
  mutate(
    roi_per_customer = mean_spend,
    total_potential_revenue = mean_spend * n
  ) %>%
  select(campaign_variant, n, mean_spend, total_spend, roi_per_customer)

print(campaign_roi)

# Statistical significance
cat("\nStatistical significance of differences:\n")
print(tukey_result)
```

---

# Session Information

```{r session-info}
sessionInfo()
```